Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
small

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach, we verify and synthesise 
a controller over $k$ time steps. We then compute a completeness threshold, $\overline{k}$,
for this controller, and verify the controller's correctness to $\overline{k}$ time steps.
Essentially, $\overline{k}$ represents the number of iterations 
required to sufficiently unwind the closed-loop state-space system 
such that the boundaries are not violated for any $k>\overline{k}$
(i.e. it's sufficient to unwound the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).

@@

2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps. 
This check is potentially unsound because we consider the currently
assumed $<I_p,F_p>$, $k$ and sampling rate.

@@

4. The third {\sc verify} stage, {\sc complete}, checks that the
current $k$ is large enough to ensure that the boundaries are not
violated for any $k'>k$.  For this purpose, we compute the
completeness threshold $\overline{k}$ for the current candidate $K$
and check that $k{\leq}\overline{k}$.

>>>>

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach, we verify and synthesise 
a controller over $k$ time steps. We then compute a completeness threshold, $\overline{k}$,
for this controller, and verify the controller's correctness to $\overline{k}$ time steps.
Essentially, $\overline{k}$ represents the number of iterations 
required to sufficiently unwind the closed-loop state-space system 
such that the boundaries are not violated for any $k{>}\overline{k}$
(i.e. it's sufficient to unwound the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).

@@

2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps. 
This check is potentially unsound because we consider the currently
assumed $\langle I_p,F_p\rangle$, $k$ and sampling rate.

@@

4. The third {\sc verify} stage, {\sc complete}, checks that the
current $k$ is large enough to ensure that the boundaries are not
violated for any $k'{>}k$.  For this purpose, we compute the
completeness threshold $\overline{k}$ for the current candidate $K$
and check that $k{\leq}\overline{k}$.
